---
title: "RestaurantVisitorPrediction.Rmd"
author: "Subramanya"
date: "11/30/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(dplyr)
library(tibble)
library(tidyr)
library(stringr)

library(ggplot2)
```

```{r cache=TRUE}
air_stores <- fread("../input/air_store_info.csv", data.table = FALSE, stringsAsFactors = TRUE)
air_visits <- fread("../input/air_visit_data.csv", data.table = FALSE, stringsAsFactors = TRUE)
air_reserve <- fread("../input/air_reserve.csv", data.table = FALSE, stringsAsFactors = TRUE)
hpg_reserve <- fread("../input/hpg_reserve.csv", data.table = FALSE, stringsAsFactors = TRUE)
hpg_stores <- fread("../input/hpg_store_info.csv", data.table = FALSE, stringsAsFactors = TRUE)
store_mapping <- fread("../input/store_id_relation.csv", data.table = FALSE, stringsAsFactors = TRUE)
holidays <- fread("../input/date_info.csv", data.table = FALSE, stringsAsFactors = TRUE)
submission <- fread("../input/sample_submission.csv", data.table = FALSE, stringsAsFactors = TRUE)
```

## Dimensioning
### Air Stores
```{r}
summary(air_stores)
glimpse(air_stores)
```

### Air Visits
```{r}
summary(air_visits)
glimpse(air_visits)
```

### Air Reserve
```{r}
summary(air_reserve)
glimpse(air_reserve)
```

### HPG Reservations
```{r}
summary(hpg_reserve)
glimpse(hpg_reserve)
```

### HPG Stores
```{r}
summary(hpg_stores)
glimpse(hpg_stores)
```

### Store Mapping
```{r}
summary(store_mapping)
glimpse(store_mapping)
```

### Holidays
```{r}
summary(holidays)
glimpse(holidays)
```


## Data Manipulation
#### Air Stores
* Convert Genre Name & Store Id to Factor
```{r}
# Convert to Dates
air_visits$visit_date <- ymd(air_visits$visit_date)
air_reserve$reserve_datetime <- ymd_hms(air_reserve$reserve_datetime)
air_reserve$visit_datetime <- ymd_hms(air_reserve$visit_datetime)

hpg_reserve$reserve_datetime <- ymd_hms(hpg_reserve$reserve_datetime)
hpg_reserve$visit_datetime <- ymd_hms(hpg_reserve$visit_datetime)

holidays$calendar_date <- ymd(holidays$calendar_date)
holidays$day_of_week <- weekdays(holidays$calendar_date)

```

### Submission
```{r}
dim(submission)
head(submission)
```
Submission contains 32019 rows.

Submission contains the data we need to predict - It contains Store IDs for which we have to predict Number of visitors on given days.  
Currently, `store_id` and `date` are joined together in to one column called `id`. Lets split it in to `store_id` and `date`

```{r}
submission <- extract(data = submission, col = id, into = c("store_id", "date"), 
                      regex = "(.{3}_.{16})_(\\d{4}-\\d{2}-\\d{2})")
submission$store_id <- factor(submission$store_id)
submission$date <- ymd(submission$date)
```

Check how many unique Store IDs are respresented for Submission

```{r}
unique_store_submissions <- unique(submission$store_id)
unique_store_submissions_df <- as.data.frame(unique_store_submissions)
names(unique_store_submissions_df) <- c("store_id")
length(unique_store_submissions)
```
There are 821 stores for which we have to Predict the Visitor Data

Check whether Store IDs are all `air` IDs or do they also contain `hpg` IDs
```{r}
unique(sapply(submission$store_id, function(x){str_extract(x, "(.{3})")}))
```
We see that all the Store IDs are `air` Ids

What is the date range for which we have to predict?
```{r}
summary(submission$date)
```

We have to predict from 4/23 to 5/31 of 2017


## Exploratory Data Analysis
#### Store-wise
#### 

Lets try to compare how many of the Stores we have to predict is available in the data
```{r}
length(intersect(air_stores$air_store_id, unique_store_submissions))
nrow(semi_join(unique_store_submissions_df, air_stores, by=c("store_id" = "air_store_id")))

```
Note that All 821 Unique stores we have to Submit data for are present in `air_stores`


